Bare Demo of IEEEtran.cls\\ for IEEE Conferences

### 2016-11-30 paper.tex
More problems with figures
And paragraph rearranged to avoid repetitions and eliminating non-necessary information.

A tutorial was developed to
obtain the necessary data using Protoboard, a web-based environment,
whose latest version can be found online at
http://python.protoboard.org/, used for learning to
program. Protoboard has the functionality described in Section
\ref{sec:method} and shown schematically in Figure 1. % This should be
                                % a reference and I'm not sure which
                                % one, if it's now Fig 1 or 2. - JJ
Users log in to 
Protoboard using their account credentials from a popular social network
(Facebook).  The web tutorial begins with three introductory videos that explain
the fundamentals of programming in Python, and how to solve the programming
exercises in the course. What follows after these videos, are 13 programming
exercises that the students need to solve in consecutively. Exercises are of
incremental difficulty. In Figures 2 and 3, % 3 is keystroke
                                % dynamics. Please revise all these
                                % Figure thing. 
 the interface of this platform is
presented. For this experiment Protoboard was configured to allow unlimited
tries to solve an exercise.

A total of 55 volunteers, with no previous experience in Python, where recruited
as a response to three announcements in a special interest group of programming
students in a social network. Learners were required to login with their
Facebook credentials, this had the advantage of not requiring the system to
maintain users’ credentials or profile information as this is kept outside in an
external service. Unfortunately this decision also kept some prospects from
volunteering; a subject reported that he normally creates temporary email
accounts to try new web services. Other requirement was that they where all
adults, this age is 18 years in Mexico where the experiment was conducted. The
requirement of the social network account stopped several prospects from
volunteering, but on the other hand gave researchers access to public
information about the subjects. All the learners were either current students or
graduates of Computer Systems Engineering. Their ages were in the range of 18 to
30 years old. Although no experience in software programming was needed, as the
web tutorial's course is of a very basic level, all the participants were
required had completed at least one course in software programming. Results from
the initial survey are shown in Figure 4.
\begin{table*}[!t]
\centering
\caption{The performance of the classifiers.}
    \begin{tabular}{ | c | l | l | l | l | }
    \hline
    Affect          & Naïve Bayes           & J-48                & k-NN              & ANN \\
    \hline
    Flow/engaged    & 79.00\% (0.11) 0.50   & 80.48\% (0.10) 0.51 & 76.14(0.09) 0.43    & 78.43(0.12) 0.45 \\
    \hline
    Relaxation      & 71.10\% (0.09) 0.40   & 72.57\% (0.11) 0.45 & 69.14\%(0.08)  0.37 & 71.24\%(0.07)  0.34\\
    \hline
    Distraction     & 70.33\% (0.13)  0.43  & 71.00\% (0.10) 0.43 & 74.00\%(0.06)  0.50 & 72.52\%(0.07)  0.39\\
    \hline
    Frustration     & 74.71\% (0.09) 0.49   & 73.86\% (0.12) 0.45 & 72.62\%(0.09)  0.42 & 78.0\%(0.09)  0.51 \\
    \hline
    Boredom         & 74.71\% (0.13) 0.47   & 84.57\% (0.06) 0.59 & 83.81\%(0.06)  0.58 & 76.19\%(0.09)  0.45\\
    \hline
    \end{tabular}
\end{table*}

>>>>

A tutorial was developed to
obtain the necessary data using Protoboard, a web-based environment,
whose latest version can be found online at
http://python.protoboard.org/, used for learning to
program. Protoboard has the functionality described in Section
\ref{sec:method} and shown schematically in Figure 1. % This should be
                                % a reference and I'm not sure which
                                % one, if it's now Fig 1 or 2. - JJ
Users log in to 
Protoboard using their account credentials from a popular social network
(Facebook), with the advantage that we did not have to keep these
credentials on site.  The web tutorial begins with three introductory videos that explain
the fundamentals of programming in Python, and how to solve the programming
exercises in the course. What follows after these videos, are 13 programming
exercises that the students need to solve in consecutively. Exercises are of
incremental difficulty. In Figures 2 and 3, % 3 is keystroke
                                % dynamics. Please revise all these
                                % Figure thing. 
 the interface of this platform is
presented. For this experiment Protoboard was configured to allow unlimited
attempts to solve an exercise.

A total of 55 volunteers, with no previous experience in Python, where recruited
as a response to three announcements in a special interest group of programming
students in a social network, but the fact that they needed Facebook kept some prospects from
volunteering; a subject reported that he normally creates temporary email
accounts to try new web services; however, the use of Facebook gave researchers access to public
information about the subjects:  all the learners were either current students or
graduates of Computer Systems Engineering. Their ages were in the range of 18 to
30 years. Although no experience in software programming was needed, as the
web tutorial's course is of a very basic level, all the participants were
required had completed at least one course in software programming. Results from
the initial survey are shown in Figure 4. %Please use reference. Fig 4
                                %is completed activities. I think this
                                %should be Fig 5. 
\begin{table*}[!t]
\centering
\caption{The performance of the classifiers.}
    \begin{tabular}{ | c | l | l | l | l | }
    \hline
    Affect          & Naïve Bayes           & J-48                & k-NN              & ANN \\
    \hline
    Flow/engaged    & 79.00\% (0.11) 0.50   & 80.48\% (0.10) 0.51 & 76.14(0.09) 0.43    & 78.43(0.12) 0.45 \\
    \hline
    Relaxation      & 71.10\% (0.09) 0.40   & 72.57\% (0.11) 0.45 & 69.14\%(0.08)  0.37 & 71.24\%(0.07)  0.34\\
    \hline
    Distraction     & 70.33\% (0.13)  0.43  & 71.00\% (0.10) 0.43 & 74.00\%(0.06)  0.50 & 72.52\%(0.07)  0.39\\
    \hline
    Frustration     & 74.71\% (0.09) 0.49   & 73.86\% (0.12) 0.45 & 72.62\%(0.09)  0.42 & 78.0\%(0.09)  0.51 \\
    \hline
    Boredom         & 74.71\% (0.13) 0.47   & 84.57\% (0.06) 0.59 & 83.81\%(0.06)  0.58 & 76.19\%(0.09)  0.45\\
    \hline
    \end{tabular}
\end{table*}
